---
title: "Q2"
output:
  pdf_document: default
  word_document: default
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, comment = "",kill_prefix=list(comment=NA, null_prefix=TRUE))
```

##  Question 2
 Import this Google sheet in R/Python and for each of the parameters (P1 to P10)
 perform a t-test and ANOVA. Share the link of your results and the script.\
 
## installing packages required for the operations performed\
### googlesheets4 is used for read the data from google sheets\
### tidyverse is usedl to redhaping the data from wide to long\
### dplyr is used for data manipulations\
### tinytex is used for get the output in pdf format\
### knitr is used for output format and styles\
### rmarkdown is used for create and genarate rmarkdown files
\
```{r packs}
library(dplyr)
library(ggplot2)
library(tidyverse)
library(googlesheets4)
library(rmarkdown)
library(knitr)
library(tinytex)
```
\newpage
## To read the data from google sheets and printing the raw data 
\
```{r data, null_prefix=T}
df <-read_sheet("https://docs.google.com/spreadsheets/d/1ndg1XMmiTsMLITNCPTapVX6Uid6H99mctIC--6DPM2Q/edit#gid=0")

print.data.frame(df)
```
\newpage
### To transform the data from wide to long to arrange the data to perform ttest  
\
```{r reshape}
ldf <- as.data.frame(df %>% gather("Group A -Sample1", "Group A -Sample2", "Group A -Sample3",
                                   "Group B -Sample1", "Group B -Sample2", "Group B -Sample3",
                                   "Group B-Sample4",  "Group C-Sample1",  "Group C-Sample2",
                                   "Group C-Sample3", key=cat, value=conc))

ldf$Parameter <- as.factor(ldf$Parameter)
ldf$group <-as.factor(substr(ldf$cat, 7,7))
ldf$sample <-as.numeric(gsub("\\D", "", ldf$cat))
ldf$id <- paste(ldf$Parameter,ldf$group, sep = "_")
```
\
### To calcualte the count, mean and sd for each parameter by group wise  
\
```{r descriptives}
ls <-ldf %>%  group_by(Parameter,group) %>%
  summarise(n = n(), avg = mean(conc), sd = sd(conc))

print.data.frame(ls)
```
\
### data subsetting for each group individually  
\
```{r subset,null_prefix=T}
ldf_a <- ldf[ldf$group=="A",]
ldf_b <- ldf[ldf$group=="B",]
ldf_c <- ldf[ldf$group=="C",]
```
\newpage
### Applying ttest for each parameter different combination A vs B, A vs C and B vs C  
\
```{r ttest}
for(i in levels(ldf$Parameter)){
  str<- as.character(i)
  
  cat("Two sample T-test for A vs B for: ", i, "\n")
  
  print(t.test(ldf_a[ldf_a$Parameter==str, "conc"], ldf_b[ldf_b$Parameter==str,"conc"], 
         alternative = "two.sided", var.equal = FALSE))
  cat(rep("_", 70))
  writeLines("\n")
  
  cat("Two sample T-test for A vs C for: ", i, "\n")
  
  print(t.test(ldf_a[ldf_a$Parameter==str, "conc"], ldf_c[ldf_c$Parameter==str,"conc"], 
              alternative = "two.sided", var.equal = FALSE))
  cat(rep("_", 70))
  writeLines("\n")
  
  cat("Two sample T-test for B vs C for: ", i, "\n")
  print(t.test(ldf_b[ldf_b$Parameter==str, "conc"], ldf_c[ldf_c$Parameter==str,"conc"], 
               alternative = "two.sided", var.equal = FALSE))
  cat(rep("_", 70), "\n" )
  writeLines("\n")
}

```
\newpage
# ANOVA for each Parameter

##In the ANOVA tables the significance of the ANOVA model was specified as following\

### Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1\

###‘***’ means statistically significant at 0% level of significance and reject the H0: Means are equal for all groups\

###‘**’ means statistically significant at 0.001% level of significance and reject the H0: Means are equal for all groups\

###‘*’ means statistically significant at 1% level of significance and reject the H0: Means are equal for all groups\

###‘*’ means statistically significant at 5% level of significance and reject the H0: Means are equal for all groups\

###‘.’ means statistically significant at 10% level of significance and reject the H0: Means are equal for all groups\

###‘ ’ means statistically significant at 100% level of significance(there was no statistical significance) and accept the H0: Means are equal for all groups
\
```{r ANOVA}
for(i in levels(ldf$Parameter)){
  par <- i
  cat("ANOVA for: ", i, "\n")
  m <- aov(conc~group, ldf[ldf$Parameter==par, ])
  print(summary(m))
  print(TukeyHSD(m))
  cat(rep("_", 70), "\n")
  writeLines("\n")
}
```


xelatex("q2.Rmd")
```{r output, echo=F}

```
